Automated Topic Naming

### 2011-09-06 ese/ese.tex
spell checking

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent dirichlet allocation \and Topic models}

@@

Using our three word-lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labelled our topics with an NFR where there was a match between a word in
the list and the same word somewhere in the distribution of words that constitute the topic.
A \emph{named topic} is a topic with a match. 
\emph{Unnamed topics} occur where there is no such match. 
This may indicate either a lack of precision in the word-lists, or simply that this topic is not associated with non-functional
requirements.
All experiments were run on the datasets for each project (e.g., PostgreSQL, MySQL, MaxDB). LDA
extracted $20$ topics per period for each project.
% Is this good enough
This labelling is \emph{semi-unsupervised} because the corpus is not derived from 
the project being analyzed, and we did not label the project's topics
ourselves for a training set. The motivation behind this technique is that
because most software often addresses similar issues, we can use the 
domain knowledge of software to label relevant topics.

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182/305/748 -- MySQL, MaxDB and Postgresql topics) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always more poor than the other two systems. The
reason for this lack of performance could be that the number of
topics, $N$ could be non-optimal for PostgreSQL. Perhaps topics were
getting too mixed and it was becoming hard to distinguish one topic
from the next. PostgreSQL's dataset was the largest of the 3 projects:
the XML data-dump that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

@@

By contrast, the PostgreSQL timeline  (Figure \ref{fig:pgsql-timeline}) is extracted from a central trunk and is not version-specific. Therefore development 
tends to be focused on releases 7.3, 7.4 and 7.5/8.0 alpha. For example, a priority for the 8.0 candidate was a Windows-native port of the source code, which seems to 
correlate with the \emph{portability} NFR increasing in frequency in mid-2004. Before the 7.4 release, \emph{usability,functionality} and \emph{portability} all 
increase in frequency, possibly reflecting the interest in adding features and documentation for the release.

@@

Given the top 15 PostgreSQL developers we found that proportionally many
developers had a focus on NFR topics. Authors with top proporitions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that yes indeed there was often a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.

>>>>

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent Dirichlet allocation \and Topic models}

@@

Using our three word-lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labelled our topics with an NFR where there was a match between a word in
the list and the same word somewhere in the distribution of words that constitute the topic.
A \emph{named topic} is a topic with a match. 
\emph{Unnamed topics} occur where there is no such match. 
This may indicate either a lack of precision in the word-lists, or simply that this topic is not associated with non-functional
requirements.
All experiments were run on the data-sets for each project (e.g., PostgreSQL, MySQL, MaxDB). LDA
extracted $20$ topics per period for each project.
% Is this good enough
This labelling is \emph{semi-unsupervised} because the corpus is not derived from 
the project being analyzed, and we did not label the project's topics
ourselves for a training set. The motivation behind this technique is that
because most software often addresses similar issues, we can use the 
domain knowledge of software to label relevant topics.

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
\emph{correctness} (182/305/748 -- MySQL, MaxDB and PostgreSQL topics) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were associated with fewer than ten topics. 
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always more poor than the other two systems. The
reason for this lack of performance could be that the number of
topics, $N$ could be non-optimal for PostgreSQL. Perhaps topics were
getting too mixed and it was becoming hard to distinguish one topic
from the next. PostgreSQL's data-set was the largest of the 3 projects:
the XML data-dump that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

@@

By contrast, the PostgreSQL time-line  (Figure \ref{fig:pgsql-timeline}) is extracted from a central trunk and is not version-specific. Therefore development 
tends to be focused on releases 7.3, 7.4 and 7.5/8.0 alpha. For example, a priority for the 8.0 candidate was a Windows-native port of the source code, which seems to 
correlate with the \emph{portability} NFR increasing in frequency in mid-2004. Before the 7.4 release, \emph{usability,functionality} and \emph{portability} all 
increase in frequency, possibly reflecting the interest in adding features and documentation for the release.

@@

Given the top 15 PostgreSQL developers we found that proportionally many
developers had a focus on NFR topics. Authors with top proportions per NFR
were:
\texttt{dennis} for usability; 
\texttt{scrappy} and \texttt{meskes} for portability;
\texttt{inoue} and \texttt{neilc} for efficiency;
\texttt{jurka} and \texttt{joe} for reliability;
\texttt{thomas} and \texttt{weick} for functionality;
and \texttt{ishii} and \texttt{scrappy} for maintainability.
Given these results we found that yes indeed there was often a focus
of $1/3$ to $1/10$ of commits dedicated to a particular NFR.
